Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-06-13 paper/paper.tex
Add voltage clamp citations

"xolotl" can recapitulate the results of voltage clamp experiments (\cite{turrigianoSelectiveRegulationCurrent1995, swensenMultiplePeptidesConverge2000, swensenModulatorsConvergentCellular2001, destexheDynamicClampPrinciplesApplications2009}). Figure \ref{fig:figureclamp} displays steps in the procedure to clamp the membrane potential of a cell with delayed rectifier potassium conductance. During an \textit{in-vitro} experiment, confounding currents would be pharmacologically-blocked and two-electrode voltage clamp used to record tail currents at fixed membrane potential (\cite{connorInwardDelayedOutward1971, connorVoltageClampStudies1971}).

>>>>

"xolotl" can recapitulate the results of voltage clamp experiments (\cite{turrigianoSelectiveRegulationCurrent1995, swensenMultiplePeptidesConverge2000, swensenModulatorsConvergentCellular2001, destexheDynamicClampPrinciplesApplications2009}). Voltage clamp represents a condition in which the membrane potential does not change from a value set by the experimenter, permitting the voltage-dependence of ion channels and their currents to be explicitly studied. Channels flux ions until the electrochemical gradient across the membrane is zero. Voltage current permits current traces to be gathered at various holding potentials, to characterize the current in isolation, or in combination with other currents (\cite{coleIonsPotentialsNerve1955, coleIonicCurrentMeasurements1960, hodgkinEffectSodiumIons1949, hodgkinMeasurementCurrentvoltageRelations1952a}).

Figure \ref{fig:figureclamp} displays steps in the procedure to clamp the membrane potential of a cell with delayed rectifier potassium conductance. During an \textit{in-vitro} experiment, confounding currents would be pharmacologically-blocked and two-electrode voltage clamp used to record tail currents at fixed membrane potential (\cite{connorInwardDelayedOutward1971, connorVoltageClampStudies1971}).
